# (PART) Honors Supplement {-}

# Honors Overview

This is the supplemental syllabus for the honors section of SOC 1120-02 (i.e. SOC 1120-02H). Students enrolled in the honors section are expected to complete all [readings](/lecture-schedule.html) and [assignments](/assignments-and-grading.html) included in the syllabus and should look to the previous sections [general course policies](/course-policies.html) as well. The following sections detail the additional work expected of students in the honors section.

## In-Depth Seminars

```{block, type = "rmdtip"}
Seminar attendance and participation is captured in the Honors Participation grade, which is worth **6.25%** of your final grade
```

You are expected to complete three seminars over the course of the semester. The goal of the seminars is to go more in-depth on several topics covered during the class and to provide an additional series of venues to develop your analytic and communication skills. Each seminar will consist of three interrelated parts:

1.  in-depth readings,
2.  a group seminar meeting, and
3.  a short response paper.

Seminar topics will be selected by the students as a group, and should align with [the topics listed below](/honors-seminar-topics.html). Consensus on seminar topics should be reached by class on Wednesday, September 5^th^. All students will complete the same seminars. Once the seminars are selected, Chris will provide a list of additional journal articles and book chapters to read. You will be expected to retrieve readings from SLU's Library if they are available there. If they are not, Chris will provide everyone with a `pdf` copy of the readings. Approximately 40 to 50 pages of additional reading per seminar should be expected.

We will schedule a when all students are available to meet together and discuss the assigned readings. Each seminar meeting will occur after the lectures on the seminar topic (ideally later that week or the next week). Chris will coordinate scheduling the seminar meetings, which will take place in one of the Sociology Department's conference rooms. You should come to seminar meetings prepared to discuss the readings themselves and draw analytic connections to the course material from both the related week and prior weeks. Attendance and participation in the seminars themselves will be factored into your honors participation grade.

### Paper Format

These discussions should inform a response paper written by each student that connects a theme from the in-depth readings and the specific content of the papers to the course as a whole. The paper should be formatted using the following guidelines:

* Times New Roman font
* 12 point font size
* Double spaced
* 1" margins on top, bottom, and sides
* Papers should be no less than four and no longer than five pages in length
* Papers should use in-text, parenthetical citations formatted using American Sociological Association (ASA) standards
* Papers should include a works cited section on a separate page that is properly formatted using ASA standards

### Grading

```{block, type = "rmdtip"}
Your papers are collectively worth **25%** of your final grade
```

Paper due-dates will be a week after each seminar meeting, and papers will be submitted via Google Classroom. Each response paper will be graded on four elements:

1.  Content (40 points): How well does the paper synthesize information
    from the in-depth readings, other course readings, the course
    lectures, and other course resources such as documentaries (as
    appropriate).
2.  Organization (15 points): How well organized is the paper? Does it
    have an introduction, a conclusion, and a thesis?
3.  Writing (15 points): How well written is the paper? Is it free of
    spelling and grammatical errors?
4.  Citations (5 points): Are citations correctly applied?

Papers are worth approximately 8.33% of your final grade for each paper.

## Op-Ed

```{block, type = "rmdtip"}
Your presentation is worth **6.25%** of your final grade
```

You should pick a topic from [the honors seminar topic list](/honors-seminar-topics.html) that you would like to use as a jumping-off point for writing an op-ed style article. With a topic in-hand, you should read ahead and pick *one narrow aspect* of the topic to focus on. Topics must be selected by March 6^th^ and are "submitted" by coming to office hours (or making an appointment to see Chris if you have a scheduling conflict) to discuss your idea.

Once you meet with Chris, you should complete additional background research on the topic, and put together a 700 to 800 word op-ed style article. This article should introduce your topic succinctly and *take a position* on it, providing specific data that supports your position. Remember that the main purpose of an op-ed is to persuade your reader. [Duke University](https://styleguide.duke.edu/toolkits/writing-media/how-to-write-an-op-ed-article/) provides some excellent guidance on forming your argument and approaching editorial writing.

Since this is an op-ed, you do not need to provide citations in the body of the paper. Please provide a works cited page on a separate page of your submission that lists all sources of data and information included in the op-ed.

### Op-Ed Seminar
Once submitted, op-eds will be shared with all honors students. Each of you should read the other op-eds and come prepared to discuss them during a final seminar session (date TBA). As with the other seminars, attendance and participation will be factored into your honors participation grade.

### Grading 
Op-eds will be submitted to Chris by the last day of class - **Monday, May 1^st^** via Google Classroom. Each op-ed paper will be graded on four elements:

1.  Content (40 points): How persuasive is the argument? What evidence is used to support the argument?
2.  Organization (15 points): How well organized is the paper? Does it
    have a clear thesis and present persuasive evidence in a clear, linear manner?
3.  Writing (15 points): How well written is the paper? Is it free of
    spelling and grammatical errors?
4.  Works Cited Page (5 points): Are citations correctly applied?

Papers are worth approximately 8.33% of your final grade for each paper.

## Honors Seminar Topics

```{r, echo=FALSE}
schedule <- data.frame(
  Week = c("02", "03", "04", "05/06", "06/07", "08", "10", "11/12", 
           "12", "13", "14", "15/16"),
  Monday = c("January 21^st^", 
             "January 28^th^", 
             "February 4^th^", 
             "February 11^th^", 
             "February 18^th^", 
             "March 4^th^",
             "March 18^th^", 
             "March 25^th^", 
             "April 1^st^", 
             "April 8^th^", 
             "April 15^th^", 
             "April 22^nd^"),
  Topic = c("Theory and Health", 
            "Culture", 
            "Socialization", 
            "Social Structure", 
            "Urban Sociology",
            "Crime & Deviance", 
            "Class & Stratification", 
            "Race & Ethnicity", 
            "Gender", 
            "The Health Care Experience", 
            "Indigenous Americans **or** Intersectionality & Health", 
            "Globalization"),
  stringsAsFactors = FALSE
)

knitr::kable(
  schedule, booktabs = TRUE,
  caption = "SOC 1120 Honors Seminar Topics"
)
```

## Honors Grading

The following point totals supersede the information on the main syllabus under Section 4.4 - "Grading" if you are enrolled in the honors section of SOC 1120.

```{r, echo=FALSE}
points <- data.frame(
  Assignment = c("Participation", "Sociological Experiences", "QHQs", "Exams", "Honors Participation", "Honors Presentation", "Honors Response Papers"),
  Points = c("25 pts", "25 pts", "50 pts", "100 pts", "25 pts", "100 pts",  "75 pts"),
  Quantity = c("x2", "x2", "x2", "x3", "x2", "x1", "x3"),
  Total = c("50 pts", "50 pts", "100 pts", "300 pts", "50 pts", "100 pts", "225 pts"),
  Percent = c("6.25%", "6.25%", "12.50%", "37.50%", "6.25%", "6.25%", "25.00%"),
  stringsAsFactors = FALSE
)

knitr::kable(
  points, booktabs = TRUE,
  caption = "SOC 1120 Honors Points Breakdown"
)
```

The information listed in Sections 4.4.1 through 4.4.3 still applies to honors students, except that incompletes are based on 660 points of work being submitted.
