# Lecture Schedule

Select a lecture from the menu to see details about topics, readings, and assignments. Additional notes and links to course materials are available through the [Google Classroom](https://classroom.google.com), which has dedicated pages for each lecture. Links to these pages are included on each lecture's reading list entry. 

The primary readings will be referred to with an abbreviation each time they appear in the reading list:

```{r, echo=FALSE}
readings <- data.frame(
  Abbreviation = c("Anderson", "*Mamma*"),
  Citation = c("Andersen, Margaret, Howard F. Taylor, and Kim A. Logio. 2016. *Sociology: The Essentials*. 9^th^ edition. Independence, KY: Cengage.", "Abraham, Laurie K. 1993. *Mama Might Be Better Off Dead: The Failure of Health Care in Urban America*. Chicago, IL: The University of Chicago Press."),
  stringsAsFactors = FALSE
)

knitr::kable(
  readings, booktabs = TRUE,
  caption = "SOC 1120 Primary Readings"
)
```

<br>
There will also be a link that refers to where a particular reading or assignment can be located:

```{r, echo=FALSE}
readings <- data.frame(
  Abbreviation = c("ER", "GC", "Link", "PL"),
  Citation = c("Electronic Reserves", "Google Classroom", "Website", "Pius Library"),
  stringsAsFactors = FALSE
)

knitr::kable(
  readings, booktabs = TRUE,
  caption = "Reading Locations"
)
```

## Week 01 {-}

### Lecture 01 - Monday, August 27^th^ {-}

#### Topics {-}

* Course Introduction

#### Readings {-}

* Andersen et al., Chapter 1 - "The Sociological Perspective" ([ER](http://eres.slu.edu/eres/coursepass.aspx?cid=4443))

#### Resources {-}

* Lecture Notes ([GC](https://classroom.google.com))
* Lecture Slides ([GC](https://classroom.google.com))

### Lecture 02 - Wednesday, August 29^th^ {-}

#### Topics {-}

* Theory and Health

#### Resources {-}

* Lecture Notes ([GC](https://classroom.google.com))

#### Documentary {-}

*  *Unnatural Causes*, Part 1 - "In Sickness and in Wealth" ([PL](http://ezp.slu.edu/login?url=http://search.ebscohost.com/login.aspx?direct=true&db=cat00825a&AN=slu.b4325118&site=eds-live))

#### Assignments Due {-}

* Entry Ticket - Student Information Sheet ([GC](https://classroom.google.com))
* Entry Ticket - Speaking Up In Class Survey ([GC](https://classroom.google.com))
