# (PART) Reading List {-}

```{r, echo=FALSE, message=FALSE}
schedule_tbl <- readr::read_csv("schedule.csv", 
                                col_types = readr::cols(
                                  module = readr::col_character(),
                                  date = readr::col_character(),
                                  start = readr::col_logical()
  ))
schedule_tbl <- dplyr::mutate(schedule_tbl, date = lubridate::mdy(date))
schedule_tbl <- dplyr::mutate(schedule_tbl, month = lubridate::month(date))
schedule_tbl <- dplyr::mutate(schedule_tbl, month = month.name[month])
schedule_tbl <- dplyr::mutate(schedule_tbl, day = lubridate::day(date))
schedule_tbl <- dplyr::mutate(schedule_tbl, dow = weekdays(date, abbreviate = FALSE))
schedule_tbl <- dplyr::mutate(schedule_tbl, label = paste0(dow, ", ", month, " ", day))

start_tbl <- dplyr::filter(schedule_tbl, start == TRUE)
```

# Course Schedule

The following is a high-level schedule that details the general topic covered by each module. Modules are collections of two or more lectures and class discussions under the broad headings provided below.

```{r, echo=FALSE}
schedule <- dplyr::tibble(
  Part = c("**1**", "1", "1", "**2**", "2", "2", "2", "**3**", "3", "3", "3", "**4**", "4"),
  Module = c("", "1", "2", "", "3", "4", "5", "", "6", "7", "8", "", "9"),
  `Planned Start Date` = c("", 
                           start_tbl$label[1], 
                           start_tbl$label[2],
                           "",
                           start_tbl$label[3],
                           start_tbl$label[4],
                           start_tbl$label[5],
                           "",
                           start_tbl$label[6],
                           start_tbl$label[7],
                           start_tbl$label[8],
                           "",
                           start_tbl$label[9]),
  Title = c("**Thinking Like Sociologists**",
            "Engaging the Social World",
            "Structuring the Social World",
            "**The Building Blocks of Society**",
            "Culture",
            "Socioeconomic Status",
            "Gender and Sexuality",
            "**The Broken Heart of America**",
            "Race and Racism",
            "Intersectionality",
            "Urban Sociology",
            "**Course Conclusion**",
            "Course Conclusion")
)

knitr::kable(
  schedule, booktabs = TRUE,
  caption = "SOC 1120 Course Overview"
)
```

### Scheduling Notes

The course schedule may change as it depends on the progress of the class and the [challenges we are confronted by this semester](covid-19.html). The web version of this document will be updated to reflect any alterations, but the `.pdf` version will remain unaltered.

This semester, we will not have class on **February 17** because it is one of the University's break days. Additionally, no class activities are scheduled for **March 10** or **May 10**. These are "flex days," which I have left without a scheduled plan to accommodate changes due to COVID-19. If we have to reschedule class days, these two dates will be used before we begin to remove content from the course plan. I will provide updates on my plans for both of these days as the semester progresses.
